The evolution of gene expression in the term placenta of viviparous mammals

### 2016-01-28 manuscript/manuscript.Rnw
make math sans
use output.top.genes.table

%\documentclass[english,12pt]{article}
\documentclass[doublespacing]{bmcart_dla}
\usepackage{fontspec}
\setmainfont{FreeSans}
\setsansfont{FreeSans}
\setmonofont{FreeMono}
%\usepackage[letterpaper,left=1in,right=1in,top=1in,bottom=1in,headheight=14pt]{geometry}
\usepackage[letterpaper]{geometry}
\usepackage{url}
% \usepackage{fancyhdr}
\usepackage{graphicx}
% \usepackage[bf]{caption}
\usepackage{rotating}
\usepackage{wrapfig}
\usepackage{booktabs}
\usepackage{float}
\usepackage{multirow}
\usepackage{setspace}
\usepackage{wrapfig}
% \usepackage{txfonts}
%\usepackage[plain]{fancyref}
\usepackage{acronym}
\usepackage{array}
\usepackage{dcolumn}
\usepackage{adjustbox}
\usepackage{longtable}
\usepackage{pdflscape}
\usepackage{amsmath}
\usepackage[backend=biber,natbib=true,hyperref=true,citestyle=numeric-comp,style=nature,autocite=inline]{biblatex}
\addbibresource{references.bib}
% \usepackage[noblocks,auth-sc]{authblk}
\usepackage[hyperfigures,bookmarks,colorlinks,linkcolor=black,urlcolor=black]{hyperref}
%\usepackage[hyperfigures,bookmarks,colorlinks,citecolor=black,filecolor=black,linkcolor=black,urlcolor=black]{hyperref}
% Floats at end for journals
% \usepackage[nolists,figuresfirst,nomarkers,heads,nofighead,notabhead]{endfloat}
% \AtBeginFigures{\newpage \section*{Figure Legends}\renewcommand{\efloatseparator}{\hbox{}}}
% \AtBeginTables{\newpage \section*{Tables}\renewcommand{\efloatseparator}{\mbox{}}}
\usepackage[nomargin,inline,draft]{fixme}
\newcommand{\DLA}[1]{\textcolor{red}{\fxnote{DLA: #1}}}
\newcommand{\DEW}[1]{\textcolor{purple}{\fxnote{DEW: #1}}}
% \usepackage[x11names,svgnames]{xcolor}
% \usepackage{texshade}
% \usepackage{tikz}
\usepackage{nameref}
\usepackage{xspace}
% this package will stretch the font slightly if necessary.
\usepackage{microtype}
\usepackage{zref-xr,zref-user}
\zxrsetup{toltxlabel}
\zexternaldocument*{supplemental_material}
\usepackage[capitalize]{cleveref}
% \newenvironment{narrow}[2]{%
%   \begin{list}{}{%
%       \setlength{\topsep}{0pt}%
%       \setlength{\leftmargin}{#1}%
%       \setlength{\rightmargin}{#2}%
%       \setlength{\listparindent}{\parindent}%
%       \setlength{\itemindent}{\parindent}%
%       \setlength{\parsep}{\parskip}}%
%   \item[]}{\end{list}}
% \def\newblock{\hskip}
% \newenvironment{paperquote}{%
%   \begin{quote}%
%      \it
%   }%
%   {\end{quote}}
% \renewcommand{\textfraction}{0.15}
% \renewcommand{\topfraction}{0.85}
% \renewcommand{\bottomfraction}{0.65}
% \renewcommand{\floatpagefraction}{0.60}
%\renewcommand{\baselinestretch}{1.8}
% \newenvironment{enumerate*}%
%   {\begin{enumerate}%
%     \setlength{\itemsep}{0pt}%
%     \setlength{\parskip}{0pt}}%
%   {\end{enumerate}}
% \newenvironment{itemize*}%
%   {\begin{itemize}%
%     \setlength{\itemsep}{0pt}%
%     \setlength{\parskip}{0pt}}%
%   {\end{itemize}}
% \setcounter{tocdepth}{3}
% \oddsidemargin 0.0in 
% \textwidth 6in
% \raggedbottom
% \clubpenalty = 10000
% \widowpenalty = 10000
% set a large emergency stretch to avoid issues with overfull boxes
% \setlength{\emergencystretch}{20em}
% make the afill smaller
% \renewcommand\Affilfont{\itshape\small}
\renewcommand\cite[1]{\autocite{#1}}
% \pagestyle{fancy}

@@

tree.id <-
    genes.to.tree[combined.fpkm[gene_short_name=="FSTL1" & species=="homo sapiens",gene_id],tree]
gene.tree.table <- trees[[tree.id]]$table
gene.tree.expression <- combined.fpkm[gene_id %in% gene.tree.table[,gene_id]]
gene.tree <- read.tree(text=trees[[tree.id]]$tree.dat)
plot.tree.matrix(read.tree(text=trees[[tree.id]]$tree.dat),gene.tree.table,gene.tree.expression,min.fpkm=5)
@ 
\caption{\genetreeexplanation{follistatin-like 1 \textit{FSTLl1}}}
\label{fig:fstl1_evolution_tree}
\end{figure}

@@

\begin{table}
  \footnotesize
<<top.50.human.expressed.genes,echo=FALSE,results="asis">>=
top.human.genes <- top.genes.table(species.name="homo sapiens")
print(xtable(top.human.genes),
      booktabs=TRUE,
      floating=FALSE,
      sanitize.text.function=genes.table.sanitize,include.rownames=FALSE)
setkey(top.human.genes,"Gene symbol")
@ 
\caption{The top 50 genes by \ac{FPKM} in \human which are not
  annotated as Mt\_rRNA, Mt\_tRNA, rRNA or a housekeeping gene. Gene
  symbol is the gene symbol or Ensembl gene id. Human Name is the HUGO
  name corresponding to the human symbol. A complete list of all genes
  is in \cref{tab:all_homo_sapiens_placenta}.}
\label{tab:top50_human_placenta}
\end{table}

@@

\begin{table}
  \footnotesize
<<top.50.bonobo.expressed.genes,echo=FALSE,results="asis">>=
top.bonobo.genes <- top.genes.table(species.name="pan paniscus")
print(xtable(top.bonobo.genes),
      booktabs=TRUE,
      floating=FALSE,
      sanitize.text.function=genes.table.sanitize,include.rownames=FALSE)
setkey(top.bonobo.genes,"Gene symbol")
@ 
\caption{\tableexplanation{\bonobo}{tab:all_pan_paniscus_placenta}}
\label{tab:top50_bonobo_placenta}
\end{table}

@@

\begin{table}
  \footnotesize
<<top.50.spider.monkey.expressed.genes,echo=FALSE,results="asis">>=
top.spider.monkey.genes <- top.genes.table(species.name="ateles fusciceps")
print(xtable(top.spider.monkey.genes),
      booktabs=TRUE,
      floating=FALSE,
      sanitize.text.function=genes.table.sanitize,include.rownames=FALSE)
setkey(top.spider.monkey.genes,"Gene symbol")
@ 
\caption{\tableexplanation{\smonkey}{tab:all_ateles_fusciceps_placenta}}
\label{tab:top50_spider_monkey_placenta}
\end{table}

@@

\begin{table}
  \tiny
<<rodentia.lineage.specific,echo=FALSE,results="asis">>=
rod.all.lin.spec <- placenta.lineage.specific.table("rod.all")
setkey(rod.all.lin.spec,"Human Symbol")
@ 
\caption{Genes whose expression changed significantly in the Rodentia
  order as compared to all other analyzed species.}
\label{tab:rodentia_lineage_specific}
\end{table}

@@

\begin{table}[h]
  \tiny
<<top.50.mouse.expressed.genes,echo=FALSE,results="asis">>=
top.mouse.genes <- top.genes.table(species.name="mus musculus")
print(xtable(top.mouse.genes),
      booktabs=TRUE,
      floating=FALSE,
      sanitize.text.function=genes.table.sanitize,include.rownames=FALSE)
setkey(top.mouse.genes,"Gene symbol")
@ 
\caption{\tableexplanation{\mouse}{tab:all_mus_musculus_placenta}}
\label{tab:top50_mouse_placenta}
\end{table}

@@

tree.id <-
    genes.to.tree[combined.fpkm[gene_short_name=="CTSL" & species=="homo sapiens",gene_id],tree]
gene.tree.table <- trees[[tree.id]]$table
gene.tree.expression <- combined.fpkm[gene_id %in% gene.tree.table[,gene_id]]
gene.tree <- read.tree(text=trees[[tree.id]]$tree.dat)
plot.tree.matrix(gene.tree,gene.tree.table,gene.tree.expression,min.fpkm=1,
                 subtree=c("ENSMODG00000002844","ENSMUSG00000055679"))
@ 
\caption{Expression of cathespins related to \textit{CTSL} with $\mathrm{FPKM} \ge 1$}
\label{fig:cathespin_evolution_tree}
\end{figure}

@@

\begin{table}[h]
  \tiny
<<top.50.n.galili.expressed.genes,echo=FALSE,results="asis">>=
top.galili.genes <- top.genes.table(species.name="nannospalax galili")
print(xtable(top.galili.genes),
      booktabs=TRUE,
      floating=FALSE,
      sanitize.text.function=genes.table.sanitize,include.rownames=FALSE)
setkey(top.galili.genes,"Gene symbol")
@ 
\caption{\tableexplanation{\galili}{tab:all_nannospalax_galili_placenta}}
\label{tab:top50_n_galili_placenta}
\end{table}

@@

\begin{table}[h]
  \tiny
<<top.50.s.carmeli.expressed.genes,echo=FALSE,results="asis">>=
top.carmeli.genes <- top.genes.table(species.name="spalax carmeli")
print(xtable(top.carmeli.genes),
      booktabs=TRUE,
      floating=FALSE,
      sanitize.text.function=genes.table.sanitize,include.rownames=FALSE)
setkey(top.carmeli.genes,"Gene symbol")
@ 
\caption{\tableexplanation{\carmeli}{tab:all_spalax_carmeli_placenta}}
\label{tab:top50_s_carmeli_placenta}
\end{table}

@@

\begin{table}
  \footnotesize
<<top.50.dog.expressed.genes,echo=FALSE,results="asis">>=
top.dog.genes <- top.genes.table(species.name="canis familiaris")
print(xtable(top.dog.genes),
      booktabs=TRUE,
      floating=FALSE,
      sanitize.text.function=genes.table.sanitize,include.rownames=FALSE)
setkey(top.dog.genes,"Gene symbol")
@ 
\caption{\tableexplanation{\dog}{tab:all_canis_familiaris_placenta}}
\label{tab:top50_dog_placenta}
\end{table}

@@

\begin{table}
  \footnotesize
<<top.50.cow.expressed.genes,echo=FALSE,results="asis">>=
top.cow.genes <- top.genes.table(species.name="bos taurus")
print(xtable(top.cow.genes),
      booktabs=TRUE,
      floating=FALSE,
      sanitize.text.function=genes.table.sanitize,include.rownames=FALSE)
setkey(top.cow.genes,"Gene symbol")
@ 
\caption{\tableexplanation{\cow}{tab:all_bos_taurus_placenta}}
\label{tab:top50_cow_placenta}
\end{table}

@@

\begin{table}[h]
  \tiny
<<top.50.pig.expressed.genes,echo=FALSE,results="asis">>=
top.pig.genes <- top.genes.table(species.name="sus scrofa")
print(xtable(top.pig.genes),
      booktabs=TRUE,
      floating=FALSE,
      sanitize.text.function=genes.table.sanitize,include.rownames=FALSE)
setkey(top.pig.genes,"Gene symbol")
@ 
\caption{\tableexplanation{\pig}{tab:all_sus_scrofa_placenta}}
\label{tab:top50_pig_placenta}
\end{table}

@@

\begin{table}[h]
  \tiny
<<top.50.horse.expressed.genes,echo=FALSE,results="asis">>=
top.horse.genes <- top.genes.table(species.name="equus caballus")
print(xtable(top.horse.genes),
      booktabs=TRUE,
      floating=FALSE,
      sanitize.text.function=genes.table.sanitize,include.rownames=FALSE)
setkey(top.horse.genes,"Gene symbol")
@ 
\caption{\tableexplanation{\horse}{tab:all_equus_caballus_placenta}}
\label{tab:top50_horse_placenta}
\end{table}

@@

\begin{table}[h]
  \tiny
<<top.50.sheep.expressed.genes,echo=FALSE,results="asis">>=
top.sheep.genes <- top.genes.table(species.name="ovis aries",n=200)
top.sheep.genes <-
    top.sheep.genes[!grepl("\\{(7SK|.+_([SM]RP|nuc)|SNOR[AD]\\d+|U\\d+|HIST.*)\\}",
                           `Gene symbol`) &
                    !grepl("\\((7SK|.+_([SM]RP|nuc)|SNOR[AD]\\d+|U\\d+|HIST.*)\\)",
                           `Human Symbol`)
                   ,][1:50,]
print(xtable(top.sheep.genes),
      booktabs=TRUE,
      floating=FALSE,
      sanitize.text.function=genes.table.sanitize,include.rownames=FALSE)
setkey(top.sheep.genes,"Gene symbol")
@ 
\caption{\tableexplanation{\sheep}{tab:all_ovis_aries_placenta}}
\label{tab:top50_sheep_placenta}
\end{table}

@@

\begin{table}
\tiny
<<top.50.elephant.expressed.genes,echo=FALSE,results="asis">>=
top.elephant.genes <- top.genes.table(species.name="loxodonta africana")
print(xtable(top.elephant.genes),
      booktabs=TRUE,
      floating=FALSE,
      sanitize.text.function=genes.table.sanitize,include.rownames=FALSE)
setkey(top.elephant.genes,"Gene symbol")
@ 
\caption{\tableexplanation{\elephant}{tab:top50_elephant_placenta}}
\label{tab:top50_elephant_placenta}
\end{table}

@@

\begin{table}
\tiny
<<top.50.armadillo.expressed.genes,echo=FALSE,results="asis">>=
top.armadillo.genes <- top.genes.table(species.name="dasypus novemcinctus")
print(xtable(top.armadillo.genes),
      booktabs=TRUE,
      floating=FALSE,
      sanitize.text.function=genes.table.sanitize,include.rownames=FALSE)
setkey(top.armadillo.genes,"Gene symbol")
@ 
\caption{\tableexplanation{\armadillo}{tab:all_dasypus_novemcinctus_placenta}}
\label{tab:top50_armadillo_placenta}
\end{table}

>>>>

%\documentclass[english,12pt]{article}
\documentclass[doublespacing]{bmcart_dla}
\usepackage{fontspec}
\setmainfont{FreeSans}
\setsansfont{FreeSans}
\setmonofont{FreeMono}
\setmathrm{FreeSans}
\setmathsf{FreeSans}
\setmathtt{FreeSans}
%\usepackage[letterpaper,left=1in,right=1in,top=1in,bottom=1in,headheight=14pt]{geometry}
\usepackage[letterpaper]{geometry}
\usepackage{url}
% \usepackage{fancyhdr}
\usepackage{graphicx}
% \usepackage[bf]{caption}
\usepackage{rotating}
\usepackage{wrapfig}
\usepackage{booktabs}
\usepackage{float}
\usepackage{multirow}
\usepackage{setspace}
\usepackage{wrapfig}
% \usepackage{txfonts}
%\usepackage[plain]{fancyref}
\usepackage{acronym}
\usepackage{array}
\usepackage{dcolumn}
\usepackage{adjustbox}
\usepackage{longtable}
\usepackage{pdflscape}
\usepackage{amsmath}
\usepackage{sfmath}
\usepackage[backend=biber,natbib=true,hyperref=true,citestyle=numeric-comp,style=nature,autocite=inline]{biblatex}
\addbibresource{references.bib}
% \usepackage[noblocks,auth-sc]{authblk}
\usepackage[hyperfigures,bookmarks,colorlinks,linkcolor=black,urlcolor=black]{hyperref}
%\usepackage[hyperfigures,bookmarks,colorlinks,citecolor=black,filecolor=black,linkcolor=black,urlcolor=black]{hyperref}
% Floats at end for journals
% \usepackage[nolists,figuresfirst,nomarkers,heads,nofighead,notabhead]{endfloat}
% \AtBeginFigures{\newpage \section*{Figure Legends}\renewcommand{\efloatseparator}{\hbox{}}}
% \AtBeginTables{\newpage \section*{Tables}\renewcommand{\efloatseparator}{\mbox{}}}
\usepackage[nomargin,inline,draft]{fixme}
\newcommand{\DLA}[1]{\textcolor{red}{\fxnote{DLA: #1}}}
\newcommand{\DEW}[1]{\textcolor{purple}{\fxnote{DEW: #1}}}
% \usepackage[x11names,svgnames]{xcolor}
% \usepackage{texshade}
% \usepackage{tikz}
\usepackage{nameref}
\usepackage{xspace}
% this package will stretch the font slightly if necessary.
\usepackage{microtype}
\usepackage{zref-xr,zref-user}
\zxrsetup{toltxlabel}
\zexternaldocument*{supplemental_material}
\usepackage[capitalize]{cleveref}
% \newenvironment{narrow}[2]{%
%   \begin{list}{}{%
%       \setlength{\topsep}{0pt}%
%       \setlength{\leftmargin}{#1}%
%       \setlength{\rightmargin}{#2}%
%       \setlength{\listparindent}{\parindent}%
%       \setlength{\itemindent}{\parindent}%
%       \setlength{\parsep}{\parskip}}%
%   \item[]}{\end{list}}
% \def\newblock{\hskip}
% \newenvironment{paperquote}{%
%   \begin{quote}%
%      \it
%   }%
%   {\end{quote}}
% \renewcommand{\textfraction}{0.15}
% \renewcommand{\topfraction}{0.85}
% \renewcommand{\bottomfraction}{0.65}
% \renewcommand{\floatpagefraction}{0.60}
%\renewcommand{\baselinestretch}{1.8}
% \newenvironment{enumerate*}%
%   {\begin{enumerate}%
%     \setlength{\itemsep}{0pt}%
%     \setlength{\parskip}{0pt}}%
%   {\end{enumerate}}
% \newenvironment{itemize*}%
%   {\begin{itemize}%
%     \setlength{\itemsep}{0pt}%
%     \setlength{\parskip}{0pt}}%
%   {\end{itemize}}
% \setcounter{tocdepth}{3}
% \oddsidemargin 0.0in 
% \textwidth 6in
% \raggedbottom
% \clubpenalty = 10000
% \widowpenalty = 10000
% set a large emergency stretch to avoid issues with overfull boxes
% \setlength{\emergencystretch}{20em}
% make the afill smaller
% \renewcommand\Affilfont{\itshape\small}
\renewcommand\cite[1]{\autocite{#1}}
% \pagestyle{fancy}

@@

tree.id <-
    genes.to.tree[combined.fpkm[gene_short_name=="FSTL1" & species=="homo sapiens",gene_id],tree]
gene.tree.table <- trees[[tree.id]]$table
gene.tree.expression <- combined.fpkm[gene_id %in% gene.tree.table[,gene_id]]
gene.tree <- read.tree(text=trees[[tree.id]]$tree.dat)
plot.tree.matrix(read.tree(text=trees[[tree.id]]$tree.dat),gene.tree.table,gene.tree.expression,min.fpkm=5)
@ 
\caption{\genetreeexplanation{follistatin-like 1 \textit{FSTL1}}}
\label{fig:fstl1_evolution_tree}
\end{figure}

@@

\begin{table}
  \footnotesize
<<top.50.human.expressed.genes,echo=FALSE,results="asis">>=
output.top.genes.table(top.genes.table(species.name="homo sapiens"))
@ 
\caption{The top 50 genes by \ac{FPKM} in \human which are not
  annotated as Mt\_rRNA, Mt\_tRNA, rRNA or a housekeeping gene. Gene
  symbol is the gene symbol or Ensembl gene id. Human Name is the HUGO
  name corresponding to the human symbol. A complete list of all genes
  is in \cref{tab:all_homo_sapiens_placenta}.}
\label{tab:top50_human_placenta}
\end{table}

@@

\begin{table}
  \footnotesize
<<top.50.bonobo.expressed.genes,echo=FALSE,results="asis">>=
top.bonobo.genes <- top.genes.table(species.name="pan paniscus")
output.top.genes.table(top.bonobo.genes)
setkey(top.bonobo.genes,"Gene symbol")
@ 
\caption{\tableexplanation{\bonobo}{tab:all_pan_paniscus_placenta}}
\label{tab:top50_bonobo_placenta}
\end{table}

@@

\begin{table}
  \footnotesize
<<top.50.spider.monkey.expressed.genes,echo=FALSE,results="asis">>=
top.spider.monkey.genes <- top.genes.table(species.name="ateles fusciceps")
output.top.genes.table(top.spider.monkey.genes)
setkey(top.spider.monkey.genes,"Gene symbol")
@ 
\caption{\tableexplanation{\smonkey}{tab:all_ateles_fusciceps_placenta}}
\label{tab:top50_spider_monkey_placenta}
\end{table}

@@

\begin{table}
  \footnotesize
<<rodentia.lineage.specific,echo=FALSE,results="asis">>=
rod.all.lin.spec <- placenta.lineage.specific.table("rod.all")
setkey(rod.all.lin.spec,"Human Symbol")
@ 
\caption{Genes whose expression changed significantly in the Rodentia
  order as compared to all other analyzed species.}
\label{tab:rodentia_lineage_specific}
\end{table}

@@

\begin{table}[h]
  \footnotesize
<<top.50.mouse.expressed.genes,echo=FALSE,results="asis">>=
output.top.genes.table(top.genes.table(species.name="mus musculus"))
@ 
\caption{\tableexplanation{\mouse}{tab:all_mus_musculus_placenta}}
\label{tab:top50_mouse_placenta}
\end{table}

@@

tree.id <-
    genes.to.tree[combined.fpkm[gene_short_name=="CTSL" & species=="homo sapiens",gene_id],tree]
gene.tree.table <- trees[[tree.id]]$table
gene.tree.expression <- combined.fpkm[gene_id %in% gene.tree.table[,gene_id]]
gene.tree <- read.tree(text=trees[[tree.id]]$tree.dat)
plot.tree.matrix(gene.tree,gene.tree.table,gene.tree.expression,min.fpkm=1,
                 subtree=c("ENSMODG00000002844","ENSMUSG00000055679"))
@ 
\caption{\genetreeexplanation{cathespins related to \textit{CTSL}}}
\label{fig:cathespin_evolution_tree}
\end{figure}

@@

\begin{table}[h]
  \footnotesize
<<top.50.n.galili.expressed.genes,echo=FALSE,results="asis">>=
output.top.genes.table(top.genes.table(species.name="nannospalax galili"))
@ 
\caption{\tableexplanation{\galili}{tab:all_nannospalax_galili_placenta}}
\label{tab:top50_n_galili_placenta}
\end{table}

@@

\begin{table}[h]
  \footnotesize
<<top.50.s.carmeli.expressed.genes,echo=FALSE,results="asis">>=
output.top.genes.table(top.genes.table(species.name="spalax carmeli"))
@ 
\caption{\tableexplanation{\carmeli}{tab:all_spalax_carmeli_placenta}}
\label{tab:top50_s_carmeli_placenta}
\end{table}

@@

\begin{table}
  \footnotesize
<<top.50.dog.expressed.genes,echo=FALSE,results="asis">>=
output.top.genes.table(top.genes.table(species.name="canis familiaris"))
@ 
\caption{\tableexplanation{\dog}{tab:all_canis_familiaris_placenta}}
\label{tab:top50_dog_placenta}
\end{table}

@@

\begin{table}
  \footnotesize
<<top.50.cow.expressed.genes,echo=FALSE,results="asis">>=
output.top.genes.table(top.genes.table(species.name="bos taurus"))
@ 
\caption{\tableexplanation{\cow}{tab:all_bos_taurus_placenta}}
\label{tab:top50_cow_placenta}
\end{table}

@@

\begin{table}[h]
  \footnotesize
<<top.50.pig.expressed.genes,echo=FALSE,results="asis">>=
output.top.genes.table(top.genes.table(species.name="sus scrofa"))
@ 
\caption{\tableexplanation{\pig}{tab:all_sus_scrofa_placenta}}
\label{tab:top50_pig_placenta}
\end{table}

@@

\begin{table}[h]
  \footnotesize
<<top.50.horse.expressed.genes,echo=FALSE,results="asis">>=
top.horse.genes <- top.genes.table(species.name="equus caballus")
print(xtable(top.horse.genes),
      booktabs=TRUE,
      floating=FALSE,
      sanitize.text.function=genes.table.sanitize,include.rownames=FALSE)
setkey(top.horse.genes,"Gene symbol")
@ 
\caption{\tableexplanation{\horse}{tab:all_equus_caballus_placenta}}
\label{tab:top50_horse_placenta}
\end{table}

@@

\begin{table}[h]
  \footnotesize
<<top.50.sheep.expressed.genes,echo=FALSE,results="asis">>=
top.sheep.genes <- top.genes.table(species.name="ovis aries",n=200)
top.sheep.genes <-
    top.sheep.genes[!grepl("\\{(7SK|.+_([SM]RP|nuc)|SNOR[AD]\\d+|U\\d+|HIST.*)\\}",
                           `Gene symbol`) &
                    !grepl("\\((7SK|.+_([SM]RP|nuc)|SNOR[AD]\\d+|U\\d+|HIST.*)\\)",
                           `Human Symbol`)
                   ,][1:50,]
output.top.genes.table(top.sheep.genes)
@ 
\caption{\tableexplanation{\sheep}{tab:all_ovis_aries_placenta}}
\label{tab:top50_sheep_placenta}
\end{table}

@@

\begin{table}
\footnotesize
<<top.50.elephant.expressed.genes,echo=FALSE,results="asis">>=
output.top.genes.table(top.genes.table(species.name="loxodonta africana"))
@ 
\caption{\tableexplanation{\elephant}{tab:top50_elephant_placenta}}
\label{tab:top50_elephant_placenta}
\end{table}

@@

\begin{table}
\footnotesize
<<top.50.armadillo.expressed.genes,echo=FALSE,results="asis">>=
output.top.genes.table(top.genes.table(species.name="dasypus novemcinctus"))
@ 
\caption{\tableexplanation{\armadillo}{tab:all_dasypus_novemcinctus_placenta}}
\label{tab:top50_armadillo_placenta}
\end{table}
